%!TEX root = cv_ml_notes.tex
% \refstepcounter{chapter}
\chapter{Frontmatter}
% \section{Frontmatter}
\label{chap:frontmatter}

\section{Disclaimer}

these are my personal notes reviewing material for CV/M interviews. The notes contain text from Quora, as well as screengrabs from various sources including Andrew Ng's Machine Learning Course on Coursera, Wikipedia, The Computer Vision Course on Coursera, and other sources. Reproduced without permission. The notes are incomplete, work in progress, and may contain mistakes.

\section{CV Interview Topics}

\textbf{Geometric Vision} - geometric transforms, projective geometry, homography, stereo vision, epipolar geometry, fundamental and essential matrices, geometric calibration, triangulation.

\textbf{Photometric Vision} - filtering, convolution, denoising, deblurring.

\textbf{Semantic Vision} - object detection, segmentation, tracking, pose estimation, visual hull, optic flow.

\textbf{Machine Learning} - linear regression, logistic regression, generative models, svm, gaussian mixture models, boosting, neural nets.

\section{ToDos}
\begin{itemize}
% \item Correlation vs. Convolution
% \item The difference is in how the summarization iterates over the elements.
\item Total Variation
\item Visual Hull
% \item Optic Flow - Lukas-Kanade, Brox
\item Cascade Detectors
\item Face landmark detection
\item Graphcut
\item Dynamic programming for stereo matching
\item Pose Estimation from 2D-3D Matches
\item Camera translation
\end{itemize}
